Multi-target detection with application to cryo-electron microscopy

### 2019-03-10 inverse_problems/inverse_problems.tex
summary (modification)

The prime motivation of this paper emanates from the problem of reconstructing small particles using cryo-EM.
Small particles induce low signal-to-noise ratio on the micrograph, which  in turn implies that particle picking---the first step in any current cryo-EM reconstruction algorithm---is impossible. 
The main message of our recent manuscript~\cite{bendory2018toward} is that  particle picking is merely an intermediate step (although frequently very useful) and the location of individual projections are nuisance variables. The ultimate goal is to estimate the 3-D structure. 
To this end,  we employed autocorrelation analysis to estimate the structure directly from the micrograph, without particle picking. 
The numerical results in~\cite{bendory2018toward} suggest that the achieved resolution using the third-order autocorrelation is limited;  higher resolution may require computing high-order autocorrelations, which will increase the sample complexity of the problem and the algorithm's computational complexity. 
%
%In addition, the model analyzed in~\cite{bendory2018toward} is somewhat simplified. 
%A full cryo-EM model includes, in addition to the target volume,
%multiple parameters:
%the 3-D orientation distribution of molecules in the ice, the distribution of projections across the  micrograph, the noise power spectrum (which is usually colored), and  the microscope contrast-transfer function.
%These parameters will be encoded within the estimated autocorrelations.
%If those parameters are unknown, they should  be  estimated, simultaneously with the 3-D structure, by solving the polynomial system of equations. Again, estimating those parameters may require high-order autocorrelations.

>>>>

The prime motivation of this paper emanates from the problem of reconstructing small particles using cryo-EM.
Small particles induce low signal-to-noise ratio on the micrograph, which  in turn implies that particle picking---the first step in any current cryo-EM reconstruction algorithm---is impossible. 
The main message of our recent manuscript~\cite{bendory2018toward} is that  particle picking is merely an intermediate step (although frequently very useful) and the location of individual projections are nuisance variables. The ultimate goal is to estimate the 3-D structure. 
To this end,  we employed autocorrelation analysis to estimate the structure directly from the micrograph, without particle picking. 
In order to gain better understanding of the method, this paper focused on an abstraction of cryo-EM---the multi-target detection model. 
Our next goal is to reconsider the full cryo-EM model, both from theoretical and algorithmic perspectives. 
In particular, the numerical results in~\cite{bendory2018toward} suggest that the achieved resolution using the third-order autocorrelation is limited;  higher resolution may require computing high-order autocorrelations, which will increase the sample complexity of the problem and the algorithm's computational complexity.

%
%In addition, the model analyzed in~\cite{bendory2018toward} is somewhat simplified. 
%A full cryo-EM model includes, in addition to the target volume,
%multiple parameters:
%the 3-D orientation distribution of molecules in the ice, the distribution of projections across the  micrograph, the noise power spectrum (which is usually colored), and  the microscope contrast-transfer function.
%These parameters will be encoded within the estimated autocorrelations.
%If those parameters are unknown, they should  be  estimated, simultaneously with the 3-D structure, by solving the polynomial system of equations. Again, estimating those parameters may require high-order autocorrelations.
